---
title: "FMT Comms Data Exploration"
author: "Paul Hegedus"
date: '2022-07-04'
output: html_document
---

# Forward MT Communications Analysis Pt. II
Analysis by communication type addressing the questions defined in the README file. Note that this document pertains to both Forward MT and Forward MT Foundation.

# Set Up
##### Packages and Functions
```{r}
library(tidyverse)
library(googlesheets4)
googlesheets4::gs4_auth("p.hegedus@comcast.net")
source("gpath.R")
source("fmt_fxns.R")
```

Make objects with HEX codes for FMT and FMTF colors
```{r}
fmt_hex <- c("#FF8A3D", "#8C9093")             # orange, gray
fmtf_hex <- c("#06038D", "#489FDF", "#D6001C") # dark blue, light blue, red
hex <- c(fmt_hex[1], fmtf_hex[1])
```


# Email
Questions of interest are below. First some further processing.

```{r}
email
email$day_hour <- paste(email$weekday_f, email$hour_f) %>% 
  factor()
```


* What day of the week and time of day have the highest open rates, when accounting for recipients?

First some initial figures about when emails are sent. 
```{r}
ggplot(email) +
  geom_histogram(aes(x = weekday_f), stat = "count")
ggplot(email) + 
  geom_histogram(aes(x = month_f), stat = "count")
```

Now let's look at some metrics, like open rate by recipients.
```{r}
ggplot(email) + 
  geom_point(aes(x = Recipients, y = `Open Rate`))
```

Initial linear model.
```{r}
m0 <- lm(`Open Rate` ~ Recipients + day_hour, data = email)
anova(m0)
plot(m0)
summary(m0)
```


* What combination of day and time had highest open rates, when accounting for recipients?


* How does frequency of emails in a week influence open rate?



# Instagram
```{r}
insta
```

# Facebook
```{r}
fb
```

# TikTok
```{r}
tt
```
