---
title: "FMT_Comms_Analysis"
author: "Paul Hegedus"
date: "`r Sys.Date()`"
output: html_document
---

Analysis to answer the questions about the FMT and FMTF communications data. Each question addressed in text and with an accompying figure out output below.

# Setup
Packages and Functions.
```{r}
options(na.action = "na.omit")
library(tidyverse)
library(googlesheets4)
# googlesheets4::gs4_auth("p.hegedus@comcast.net")
source("fmt_fxns.R")
load("exp_dat.RData")
```


# Email

The two highest emails with open rates, not accounting for recipients, were the "Progressive happy hour", and the "School board forum reminder" with 5 and 46 recipients, respectively. These were deemed outliers and removed from the analysis below.
```{r}
email[email$open_rate_pct > 40, 
      c("Weekday", "usa_date", "ampm_time", "Email", "Recipients", "open_rate_pct")][1:2, ]
```

## Questions of Interest

* What day of the week and time of day have the highest open rates, when accounting for recipients?
* What combination of day and time had highest open rates, when accounting for recipients?
* How does frequency of emails in a week influence open rate?

First, what day of the week and time of day have the highest open rates, when accounting for recipients?

```{r}

```

Second, what combination of day and time had highest open rates, when accounting for recipients?


Third, how does frequency of emails in a week influence open rate?


# Instagram

* What day of the week and time of day have the highest engagement rate?
* What combination of day and time had highest engagement rate?
* Do graphics or photos have higher engagement rates?





