---
title: "FMT Comms Analysis"
author: "Paul Hegedus"
date: '2022-07-02'
output: html_document
---

# Forward MT Communications Analysis
Analysis by communication type addressing the questions defined in the README file. 

# Set Up
##### Packages and colors.
```{r}
library(tidyverse)
library(googlesheets4)
googlesheets4::gs4_auth("p.hegedus@comcast.net")
source("gpath.R")
source("fmt_fxns.R")

fmt_hex <- c("#FF8A3D", "#8C9093")             # orange, gray
fmtf_hex <- c("#06038D", "#489FDF", "#D6001C") # dark blue, light blue, red
hex <- c(fmt_hex[1], fmtf_hex[1])
```

# Import Data
Import data, split by type. Do some basic preparations (e.g. Weekday to character & day of week).

## Email
```{r}
## import data
fmt_e <- read_sheet(
  ss = gpath,
  sheet = "Email",
  range = "Email!A1:G68",
  col_types = "cDtcnnn") %>% 
  fixDayDateTime()
```

Initial summary statistics.
```{r}
summary(fmt_e)
```

Looks like there is missing data in 'Open Rate' & 'Time'.
```{r}
col_of_int <- c("Weekday", "usa_date", "ampm_time", 
                "Email", "Recipients", "Open Rate")
# TODO: MISSING DATA
fmt_e[is.na(fmt_e$`Open Rate`), col_of_int]
## fill gap in Time
fmt_e[is.na(fmt_e$Time), col_of_int]
fmt_e[is.na(fmt_e$Time), "ampm_time"] <- "03:30 PM"
fmt_e[is.na(fmt_e$Time), "hour"] <- "3 PM"
fmt_e[is.na(fmt_e$Time), "hour_f"] <- "3 PM"
```

```{r}
fmt_e$Org <- "FMT"
email <- fmt_e
```

## Instagram
### Forward Montana
First, the Forward Montana instagram...
```{r}
## import data
fmt_i <- read_sheet(
  ss = gpath,
  sheet = "Instagram",
  range = "Instagram!A2:H70",
  col_types = "cDtcnnnc") %>% 
  fixDayDateTime()

## standardize 'Graphic or Photo?' column
# make new col
fmt_i$g_or_p <- fmt_i$`Graphic or Photo?`
unique(fmt_i$g_or_p)
# stand. graphic
indx <- grep("^graphic$", fmt_i$g_or_p, ignore.case = TRUE)
fmt_i[indx, "g_or_p"] <- "Graphic"
# stand. photo
indx <- grep("^photo$|^Photos$", fmt_i$g_or_p, ignore.case = TRUE)
fmt_i[indx, "g_or_p"] <- "Photo"
# make 'Both' from photo and graphic
patterns <- c("^Photo & graphic$", "^Photo and graphic$", 
              "^Graphic and photo$", "^Graphic and phots$")
indx <- grep(paste(patterns, collapse = "|"), fmt_i$g_or_p, ignore.case = TRUE)
fmt_i[indx, "g_or_p"] <- "Both"
# format Video graphic 
indx <- grep("^Video graphic$", fmt_i$g_or_p, ignore.case = TRUE)
fmt_i[indx, "g_or_p"] <- "Video Graphic"

## make factor
fmt_i$g_or_p_f <- factor(
  fmt_i$g_or_p,
  levels = c("Photo", "Graphic", "Both", "Video", "Video Graphic")
)
```

Initial summary statistics.
```{r}
summary(fmt_i)
```

Looks like there is a missing 'Impressions', 'Engagements', 'Engagement rate', 'Time', and 'Graphic or Photo?.
```{r}
col_of_int <- c("Weekday", "usa_date", "ampm_time",  "Post", 
                "Impressions", "Engagements",  "Enagement rate",
                "Graphic or Photo?")
# TODO: MISSING DATA
fmt_i[is.na(fmt_i$`Enagement rate`), col_of_int]
fmt_i[is.na(fmt_i$Engagements), col_of_int]
fmt_i[is.na(fmt_i$Impressions), col_of_int]
fmt_i[is.na(fmt_i$Time), col_of_int]
fmt_i[is.na(fmt_i$`Graphic or Photo?`), col_of_int]
```


### Forward Montana Foundation
Now the Forward Montana Foundation instagram...
```{r}
## import data
fmtf_i <- read_sheet(
  ss = gpath,
  sheet = "Instagram",
  range = "Instagram!A84:H111",
  col_types = "cDtcnnnc") %>% 
  fixDayDateTime()

## standardize 'Graphic or Photo?' column
# make new col
fmtf_i$g_or_p <- fmtf_i$`Graphic or Photo?`
unique(fmtf_i$g_or_p)

## make factor
fmtf_i$g_or_p_f <- factor(
  fmtf_i$g_or_p,
  levels = c("Photo", "Graphic", "Both")
)
```

Initial summary statistics.
```{r}
summary(fmtf_i)
```

Looks like there is a missing 'Engagements', 'Time', and 'Graphic or Photo?.
```{r}
col_of_int <- c("Weekday", "usa_date", "ampm_time",  "Post", 
                "Impressions", "Engagements",  "Enagement rate",
                "Graphic or Photo?")
# TODO: MISSING DATA
fmtf_i[is.na(fmtf_i$Engagements), col_of_int]
fmtf_i[is.na(fmtf_i$`Graphic or Photo?`), col_of_int]

## fill gap in Time
fmtf_i[is.na(fmtf_i$Time), col_of_int]
fmtf_i[is.na(fmtf_i$Time) & fmtf_i$usa_date == "05/31/2022", "ampm_time"] <- "11:45 AM"
fmtf_i[is.na(fmtf_i$Time) & fmtf_i$usa_date == "05/31/2022", "hour"] <- "11 AM"
fmtf_i[is.na(fmtf_i$Time) & fmtf_i$usa_date == "05/31/2022", "hour_f"] <- "11 AM"
```


```{r}
fmt_i$Org <- "FMT"
fmtf_i$Org <- "FMTF"
insta <- rbind(fmt_i, fmtf_i)
```

## Facebook
### Forward Montana
```{r}
## import data
fmt_f <- read_sheet(
  ss = gpath,
  sheet = "FB",
  range = "FB!A2:H35",
  col_types = "cDtcnnnc") %>% 
  fixDayDateTime()

## standardize 'Graphic or Photo?' column
# make new col
fmt_f$g_or_p <- fmt_f$`Graphic or Photo?`
unique(fmt_f$g_or_p)
# stand. photo
indx <- grep("^photo$|^Photos$", fmt_f$g_or_p, ignore.case = TRUE)
fmt_f[indx, "g_or_p"] <- "Photo"

## make factor
fmt_f$g_or_p_f <- factor(
  fmt_f$g_or_p,
  levels = c("Photo", "Graphic", "Both", "Video")
)
```

Initial summary statistics.
```{r}
summary(fmt_f)
```

Looks like there is a missing 'Impressions, 'Engagements', and 'Engagement rate'.
```{r}
col_of_int <- c("Weekday", "usa_date", "ampm_time",  "Post", 
                "Impressions", "Engagements",  "Enagement rate",
                "Graphic or Photo?")
# TODO: MISSING DATA
fmt_f[is.na(fmt_f$Impressions), col_of_int]
fmt_f[is.na(fmt_f$Engagements), col_of_int]
fmt_f[is.na(fmt_f$`Enagement rate`), col_of_int]
```

### Forward Montana Foundation
Now the Forward Montana Foundation FB.
```{r}
## import data
fmtf_f <- read_sheet(
  ss = gpath,
  sheet = "FB",
  range = "FB!A44:H56",
  col_types = "cDtcnnnc") %>% 
  fixDayDateTime()

names(fmtf_f)[5] <- "Impressions"

## standardize 'Graphic or Photo?' column
# make new col
fmtf_f$g_or_p <- fmtf_f$`Graphic or Photo?`
unique(fmtf_f$g_or_p)

## make factor
fmtf_f$g_or_p_f <- factor(
  fmtf_f$g_or_p,
  levels = c("Photo", "Graphic", "Both", "Video")
)
```

Initial summary statistics.
```{r}
summary(fmtf_f)
```

Looks like there is a missing 'Graphic or Photo?'.
```{r}
col_of_int <- c("Weekday", "usa_date", "ampm_time",  "Post", 
                "Impressions", "Engagements",  "Enagement rate",
                "Graphic or Photo?")
# TODO: MISSING DATA
fmtf_f[is.na(fmtf_f$`Graphic or Photo?`), col_of_int]
```

```{r}
fmt_f$Org <- "FMT"
fmtf_f$Org <- "FMTF"
fb <- rbind(fmt_f, fmtf_f)
```


## TikTok
```{r}
## import data
tt <- read_sheet(
  ss = gpath,
  sheet = "TikTok",
  col_types = "cDtcnnn") %>% 
  fixDayDateTime()
```

Initial summary statistics.
```{r}
summary(tt)
```

# Clean Up
```{r}
rm(indx, patterns, col_of_int, fmt_e, fmt_i, fmtf_i, fmt_f, fmtf_f)
```

# Email
```{r}
email
```


# Instagram
```{r}
insta
```

# Facebook
```{r}
fb
```

# TikTok
```{r}
tt
```

